\documentclass[17pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usetheme{CambridgeUS}
\usepackage{setspace}
\onehalfspacing


\begin{document}
	\author{Wouter de Boer}
	\title{card game setup}
	%\subtitle{}
	%\logo{}
	\institute{Sogyo}
	\date{\today}
	\subject{Individual project}
	\begin{frame}[plain]
		\maketitle
	\end{frame}
	
	\begin{frame}
		\frametitle{Initials plans}

		\begin{itemize}
			\item 2 players card game.
			\item players move cards over the field.
			\item exact rules to be determined.
				\item make a setup that is scalable.
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Evolution of the plans}
	\begin{itemize}
		\item  Minimum vertical slice achieved.
		\item  Did not meet sprint goals.
		\item learning vs meeting goals.
		\item Lower demands to get things done.
	\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Architecture}
		\framesubtitle{Ruby, Ruby, Ruby. More specifically, ruby on rails.}
		\begin{itemize}
		\item Model: plain ruby
		\item View: erb-files and css
		\item Control: ruby, heavy rails dependency.
		\item Channels, for web-sockets.
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Architecture, some specifics}
		\begin{itemize}
			\item No-db (rails, please)
			\item gems: mini-test
			\item gem: turbo-frames/streams
			\item gem: pry (in the later stages)
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Objectives}
		\begin{itemize}
		\item Technical: Learning ruby/ rails
		\item Personal: Structuring a bigger project.
		\item Making choices is difficult
		\end{itemize}
	\end{frame}
	\begin{frame}
		\frametitle{Take-aways}
		\begin{itemize}
		\item Working with, against and around a framework.
		\item Minimum viable product also goes for architecture.
		\item Distinction between theoretical understanding and a working app.
		\end{itemize}
	
		
	\end{frame}
\end{document}